%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
% Resume in Latex
% Author : Shubham Mazumder
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{fontawesome}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}
\geometry{paperwidth=9in, paperheight=12in, margin=0.5in}

%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}

% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}


% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}


% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }



% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\begin{center}

    \textbf{\Large Arrabelli Varsha Reddy} \vspace{0.1cm} \\
    \textit{+91 709-311-9393} $|$  
    \href{https://varshareddyarrabelli.github.io/portfolio-website}{{\textit{Portfolio}}} $|$
    \href{mailto:varshareddyarrabelli2003@gmail.com}{{\textit{Email}}} $|$ 
    \href{https://www.linkedin.com/in/varshareddyarrabelli}{{\textit{Linkedin}}} $|$
    \href{https://github.com/varshareddyarrabelli}{{\textit{Github}}}
    \vspace{-8pt}    
\end{center}


    \vspace{0.1cm}
% -------------------------------------
%----------EXPERIENCE------------------
% -------------------------------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Calicut}{GPA : 8.5}{B.Tech in Computer Science}{December 2020 -- May 2024} 
    \resumeSubheading
      {Sri Chaitanya Junior College\hspace{1.9cm}}{\% : 93.5}{Higher Secondary Education}{May 2018 -- September 2020}
       \resumeSubheading
      {SPR School of Excellence\hspace{1.4cm}}{GPA : 9.8}{Secondary Education}{May 2018 -- September 2020}
  \resumeSubHeadingListEnd
\vspace{-0.1cm}

\section{Experience}
  \resumeSubHeadingListStart
      \resumeProjectHeading
           {\titleItem{{Software Engineer Intern}} $|$ \emph{Sandvine}}{January 2024 -- May, 2024}
      \resumeItemListStart
        \resumeItem{Developing and implementing signature-based solutions for precise 
identification and classification of specific network traffic patterns, significantly improving accuracy and efficiency.}
        \resumeItem{In-depth knowledge of various network protocols.
Vigilantly monitored and addressed network leaks, analyzing, and adding signatures for different applications of` network traffic.
}
        \resumeItem{Established a comprehensive suite of unit test cases, enhancing the reliability and efficiency of network traffic classification algorithms.}

        \resumeItem{Python / C / C++ / Wireshark}
      \resumeItemListEnd
\vspace{0.3cm}
   \resumeProjectHeading
           {\titleItem{{ML Research}} $|$ \emph{Pournami P.N. (Prof. at NIT Calicut)
}}{July 2023 -- Jan 2024}
      \resumeItemListStart    
    \resumeItem{
I was in a project under our lecturer and alongside a Ph.D. student, focused on enhancing the accuracy of image captioning models.}}
        \resumeItem{
Image captioning aims to detect information by describing the image content through image and text processing techniques.
 }
 \resumeItem{
This project focuses on the development of an image captioning system, a novel approach merging CV and NLP. Leveraging the deep learning techniques, the system generate descriptive and relevant captions for input images.}}} 
    \resumeItemListEnd
    \vspace{0.3cm}
    \resumeProjectHeading
           {\titleItem{{Software Developer Intern}} $|$ \emph{Arcesium (D.E. Shaw Group)}}{May 2023 -- July 2023}
      \resumeItemListStart
        \resumeItem{Designed and implemented a Java library facilitating dynamic runtime modifications of property values in configuration files.}
        \resumeItem{This library eliminated the need for a redeployment process, providing a seamless experience for users. The library exhibits minimal runtime and environment-specific dependencies, requiring minimal code modifications by end-users.}
        \resumeItem{Developed a front-end interface for clients that enhances the user experience, empowering clients to make real-time adjustments without extensive technical knowledge.}
        \resumeItem{Java / Spring / React js / SQL / Spring Boot / Git }
        \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-0.1cm}

\section{Technical Skills}
\subheadingtitlevspace
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \titleItem{Languages}{: C, C++, Java, Python, SQL, JavaScript, PHP, Dart} \hspace{1.2cm}
     \titleItem{Relevant Coursework}{: OS, DBMS, Computer Networks, OOPS} 
    \titleItem{Development Tools}{: Linux, Git, Github, Docker, VS code, Wireshark} \hspace{0.2cm}
 \titleItem{Frameworks}{: Flutter, Flask, Spring, Nextjs, Spring Boot} \hspace{1.2cm}
    \titleItem{Web Tools}{: HTML, CSS, React, ExpressJs, NextJs, NodeJs, MYSQL, MongoDB, Firebase} 
    }}
    
    }}
 \end{itemize}
\sectionspace

\vspace{0.2cm}

% -------------------------------------
%----------PROJECTS--------------------
% -------------------------------------

 \section{Projects}
     \resumeSubHeadingListStart
        \resumeProjectHeading
           {\titleItem{Event Management Website 
\hspace{0.35cm} \href{https://github.com/varshareddyarrabelli/Event-Management-Website}{\faGithub}} $|$ \emph{Python, Flask, SQL, HTML, CSS}}{January, 2023}
            \resumeItemListStart
            \resumeItem{The Event Management website provides students with a comprehensive view of various organization events, offering detailed event information. }
            \resumeItem{Students can share feedback for each event and access department-wise event listings. The search feature enables easy exploration of events by name and venue.}
           \resumeItemListEnd
           \vspace{0.2cm}
              \resumeProjectHeading
           {\titleItem{College Management System
\hspace{0.35cm} \href{https://github.com/varshareddyarrabelli/College-Management-System}{\faGithub}} $|$ \emph{HTML, CSS, PHP, SQL}}{October, 2022}
            \resumeItemListStart
            \resumeItem{A website that stores student and teacher records and performs different operations on the data. }
            \resumeItem{A website where we can also track students grades and course enrollment details and teachers to students mapping.}
           \resumeItemListEnd
           \hspace{0.2cm}
              \resumeProjectHeading
           {\titleItem{Events Buzz App 
\hspace{0.35cm} \href{https://github.com/varshareddyarrabelli/Event-Buzz-App}{\faGithub}} $|$ \emph{Flutter, Dart, Firebase}}{March, 2023}
            \resumeItemListStart
            \resumeItem{Discover events within the organization and access reliable information through a structured hierarchical
interface on the app. Stay informed and engaged with the event updates }
            \resumeItem{Smooth App User Interface for a better user experience.}
           \resumeItemListEnd
           \resumeItemListEnd
           \vspace{0.35cm}
     \resumeSubHeadingListEnd
\begin{minipage}[t]{0.5\textwidth}
\section{Key Skills}
\resumeItemListStart
            \resumeItem{Time Management}
            \resumeItem{Communication Skills}
            \resumeItem{Team Work}
            \resumeItem{Leadership Qualities}
           \resumeItemListEnd
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\section{Links \& Certifications}
    \resumeItemListStart
            \resumeItem{Problem solving certificate on HackerRank\hspace{0.35cm}{\href{https://www.hackerrank.com/certificates/3c21cef0360a}{\faExternalLink}}}
            \resumeItem{CSS certificate on HackerRank\hspace{0.35cm}{\href{https://www.hackerrank.com/certificates/b613f251c3fe}{\faExternalLink}}}
            \resumeItem{HackerRank Profile\hspace{0.35cm}{\href{https://www.hackerrank.com/profile/arrabelli_b20071}{\faExternalLink}}}
            \resumeItem{LeetCode Profile\hspace{0.35cm}{\href{https://leetcode.com/varshareddyarrabelliu/}{\faExternalLink}}}
           \resumeItemListEnd
\end{minipage}%
\section{Achievements}
\resumeItemListStart
            \resumeItem{Received job offers from Google, Salesforce, and Arcesium.}
            \resumeItem{Top 1 percent on leet code | Competitive Programmer with a record of consistency in algorithmic problem-solving in contests. }
            \resumeItem{Ranked amongst top 1\% in Joint Entrance Examination (JEE) Mains 2020 out of total 8.5 lakh candidates.}
            \resumeItem{ Certified and 5-star Programmer at HackerRank.}
           \resumeItemListEnd


%-------------------------------------------
\end{document}
